Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-09 paper.tex
Journal, Multiple Intelligences, Portfolios.  Finish the Personalization draft.

Choices the child has made are stored in \textit{Avatar Services},
accessible to all story modules and activities.  Past choices
can thus influence the future direction of a story.  Story module
alternatives are supported to allow learning material to presented in
different ways for different learners. Further, the record of a
child's experiences with Nell are recorded in a \textit{Journal},
which can be edited and customized by the user.  Careful arrangement
of sections of the Journal can become a Portfolio~\cite{stefanakis:portfolios}.
The journal also allows undo/redo \textbf{XXXX}.

In the future, we expect to allow further personalization via deep
recombination of story elements.  Lebowitz~\cite{lebowitz:universe85} and Riedl~\cite{riedl:planning} show how a planner can be used to recombine story
modules.  We expect to be less ambitious then previous work: instead
of attempting to generate thousands of stories from tens of templates,
we expect to modestly adapt from hundreds of story modules created
in a decentralized manner by teachers.

@@

%%  LocalWords:  personalization

>>>>

\textit{Avatar Services} stores all choices made by the child and make them
accessible to story modules and activities.  Accomplishments
(completed lessons) are also stored.  Nell can thus provide multiple
alternative story modules for a given plot point/lesson, and select
between them based on either the explicit choices made by the child
(``fractions in outer space,'' if the child previously indicated a
preference for space-themed lessons) or prior success with a given
lesson style (a large number of accomplishments in musical-rhythmic
tasks suggests a rhythmic approach to fractions).  In this manner we
can engage the child's interests and cater to different learning
styles~\cite{gardner:mi}.

Moving further, this record of past choices and accomplishments can be
reviewed.  The narrative history is stored in the \textit{Journal},
where it can form the core of a Portfolio~\cite{stefanakis:portfolios}.
In order to encourage fearless play and experimentation, the Journal
also supports pervasive undo; you can replay the narrative starting at
any past point in the journal.

In the future, we expect to allow further narrative personalization
via recombination of story elements.
Lebowitz~\cite{lebowitz:universe85} and Riedl~\cite{riedl:planning}
show how a planner can be used to recombine and adapt story fragments.
In this we expect to be less ambitious than the cited work: instead of
attempting to generate thousands of stories from tens of templates, we
expect to select and then modestly adapt from hundreds of story
modules created in a decentralized manner by teachers---and eventually
by the students themselves.

@@

%%  LocalWords:  personalization Lebowitz
